MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-05 paper/paper.tex
added ieee template just in case, and cleared paper warnings
added another paragraph explaining comparison of spectrograms

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fake_spectrogram.png}
  \caption{Spectrogram representation of a Fake Audio Sample.}
  \label{fig:real_spectrogram}
\end{figure}

>>>>

Figure~\ref{fig:real_spectrogram} portrays an example of a "real" audio sample represented as a Mel-spectrogram image. Examining the image, it is clear that it is more information-rich than its two-dimensional counterpart in Figure~\ref{fig:real_waveform}. The additional data represented here is essential to machine learning models as it becomes easier to decide on a classification. Figure~\ref{fig:fake_spectrogram} portrays an example of a "fake" audio sample represented as a Mel-spectrogram image. When comparing this image to figure~\ref{fig:real_spectrogram}, we can see there are some key differences at a glance. These two samples are good examples of their respecive classes. Not all of the generated Mel-spectrogram images in our dataset were so clear cut. Nevertheless, both classes of images encompassed key features on which the model was able to decide.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fake_spectrogram.png}
  \caption{Spectrogram representation of a Fake Audio Sample.}
  \label{fig:fake_spectrogram}
\end{figure}
